### 2011-03-16 code/subarchitectures/vision.sa/branches/post-review-yr2-11533/src/c++/vision/components/VisualLearner/test/gy2report/gy2article.tex
gy2 report, output log added

>>>>

\subsection{Example log}

This is a part of the log file that shows the state transitions while the robot
is learning one object (approximately $50s$).

\begin{verbatim}
[INFO gy2article: 4218.43 NEW STATE stTableEmpty]
[INFO gy2article: 4220.43 SCENE 357: 1081vl]
[INFO gy2article: 4220.44 **********]
[INFO gy2article: 4220.44 NEW STATE stWaitToAppear (to=20s)]
[INFO gy2article: 4222.45 STATE stWaitToAppear]
[INFO gy2article: 4226.47 **********]
[INFO gy2article: 4226.47 NEW STATE stObjectOn]
[INFO analyzer: blockVisualObjectUpdates enable=true]
[INFO gy2article: 4231.47 **********]
[INFO gy2article: 4231.47 NEW STATE stTeaching (to=10s)]
[INFO SOI.filter: blockProtoObjectUpdates enable=true]
[INFO gy2article: 4232.47 Tutor: this is elongated]
[INFO gy2article: 4232.47 **********]
[INFO gy2article: 4232.47 NEW STATE stWaitForResponse (to=15s)]
[INFO gy2article: 4234.48 STATE stWaitForResponse]
[INFO gy2article: 4234.48 Robot says: thank you]
[INFO gy2article: 4234.48 **********]
[INFO gy2article: 4234.48 NEW STATE stWaitForLearningTask (to=120s)]
[INFO gy2article: 4237.06 Learnig task added: [WMA: vision.sa:o2:J]]
[INFO gy2article: 4240.21 Learnig task changed: [WMA: vision.sa:o2:J]]
[INFO gy2article: 4240.21 A Learning Task was detected.]
[INFO gy2article: 4240.21 **********]
[INFO gy2article: 4240.21 NEW STATE stTeaching (to=10s)]
[INFO gy2article: 4241.22 Tutor: this is black]
[INFO gy2article: 4241.22 **********]
[INFO gy2article: 4241.22 NEW STATE stWaitForResponse (to=15s)]
[INFO gy2article: 4243.23 Robot says: thank you]
[INFO gy2article: 4243.23 **********]
[INFO gy2article: 4243.23 NEW STATE stWaitForLearningTask (to=120s)]
[INFO gy2article: 4249.55 Learnig task added: [WMA: vision.sa:p2:J]]
[INFO gy2article: 4256.04 Learnig task changed: [WMA: vision.sa:p2:J]]
[INFO gy2article: 4256.05 A Learning Task was detected.]
[INFO gy2article: 4256.05 **********]
[INFO gy2article: 4256.05 NEW STATE stTeaching (to=10s)]
[INFO gy2article: 4257.06 **********]
[INFO gy2article: 4257.06 NEW STATE stEndOfTeaching (to=15s)]
[INFO gy2article: 4257.08 **********]
[INFO gy2article: 4257.08 NEW STATE stUnloadScene]
[INFO analyzer: blockVisualObjectUpdates enable=false]
[INFO gy2article: 4262.10 SCENE: empty]
[INFO SOI.filter: blockProtoObjectUpdates enable=false]
[INFO gy2article: 4262.10 **********]
[INFO gy2article: 4262.10 NEW STATE stWaitToDisappear (to=20s)]
[INFO gy2article: 4264.11 STATE stWaitToDisappear]
[INFO gy2article: 4268.13 **********]
[INFO gy2article: 4268.13 NEW STATE stTableEmpty]
\end{verbatim}
